---
title: "demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LDen)
```

The data should be formatted as a data frame of artifact locations with x coordinates in the first column, y coordinates in the second, and artifact type in the third column.

```{r load data}
locations <- LDen::AZ_A1020_BLM
head(locations)
```

# Distance matrix from location data

```{r create distance matrix}
distance_test <- distance_matrix(location_data = locations)
```

# Local Counts

```{r local counts}
counts_test <- local_counts(locations, radius = 2)
```

# Local Density

```{r local density}
local_density_test <- local_density(locations, radius = 2)
```

# Global Density

site area for Kintigh's example file "LDEN.csv = 154"
the site area for "AZ_A1020_BLM_point_plots.csv" = 2409

```{r global density}
global_density_test <- glb_density(locations, site_area = 154)
```

# Single Radius

```{r lda single rad}
lda_test <- lda(locations, radius = 2, site_area = 154)
```

# Multiple radii


```{r lda multiple rad}
lda_test <- lda(locations, radius = cbind(1,2,5), site_area = 154)
```


